Clustering time series based on probability distributions across temporal granularities

### 2021-11-08 main.Rmd
change the application graph
adding tsne plot

@@

```{r opt-clusters}
```

@@

```{r hod-ind-group, fig.cap = "The distribution of selected customers over hod (a), moy (b), and wnwd (c) for the $24$ selected customers is shown. In each case, the same colour denotes the same group using js-based clustering and are placed together to facilitate comparison. Individuals with similar distributional differences across categories of hod or moy are grouped together, with some exceptions. Distributional differences across categories of wnwday are not discernable except for a couple of customers." }
```

>>>>

```{r tsne-plot}
```

@@

```{r opt-clusters-jsd}

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the 24 customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size $k$"}

@@

```{r hod-ind-group, fig.cap = "The distribution of selected customers over hod (a), moy (b), and wnwd (c) for the $24$ selected customers is shown. In each case, the same colour denotes the same group using js-based clustering and are placed together to facilitate comparison. Individuals with similar distributional differences across categories of hod or moy are grouped together, with some exceptions. Distributional differences across categories of wnwday are not discernable except for a couple of customers.", fig.height =  3.5}
```
